---
title: "Make interactive html without shiny"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

<style>                     
.navbar-brand {
color:black!important;
}
</style>           

```{r setup, include=FALSE}
library(ggplot2)
library(ggrepel)
library(DT)
library(plotly)
```

Description of this html file
=======================================================================

<b><font face="Georgia" size="3em" color="#000000"> This file includes interactive tables showing association testing results and interactive plots showing pathway enrichment test results. </font></b>


Visualization of Statics Plots
============================================================================
<b><font face="Georgia" size="3em" color="#000000"> * Static plots based on the data including both sex</font></b>  


Row{data-height=550}
-----------------------------------------------------------------------
### *
```{r}
readPath <- "***"
load(paste0(readPath,"this.Rdat"))

IPSvsC1
```

### *
```{r}
IPSvsC2
```

Row{data-height=550}
-----------------------------------------------------------------------
### *
```{r}
IPSvsC3
```

### *
```{r}
IPSvsC4
```

Association Test Results
=======================================================================
Row{data-height=500}
-----------------------------------------------------------------------
### <b><font face="Georgia" size="3em" color="#000000"> 1. both sex </font></b> <b><font face="Georgia" size="3em" color="#000000"> * Including covariates</font></b> 

```{r}
table1 <- read.csv(paste0(readPath,"/table1.txt"),sep="\t")
DT::datatable(table1[,-2],filter="top", options = list(pageLength = 15))
```

Pathway Enrichment test
=======================================================================
```{r}

resourceLabel <- c("A","B","C","D","E","F","G")



whichItem <- "HallMark"
load(paste0(pathIn,"whichItem",".pDat.Rdat"))

plot_ly(pDat,
        type = 'scatter',
        mode = 'markers',
        x = ~ factor(resource,levels=resourceLabel),
        y = ~pathway,       
        marker = list(size = ~-log(pval),sizeref = 0.3,sizemode = 'area',
                      color= ~NES,color=seq(0, 39),
                      sizebar=list(title="-log(pvalue)"),
                      colorbar=list(title='NES'),
                      colorscale='Viridis',
                      reversescale =T),
        text = ~disPro, ### pre-extract the leading edges
        hovertemplate = paste(  
          "<b>pathway: %{y}</b><br><br>",
          "<b>%{x}</b><br><br>",
          "leading edge: %{text}",
          "<extra></extra>")
) %>% layout(title = paste0(paste0("Enrichment test based on ",whichItem, " database")),
             xaxis = list(title = "", tickangle = -20,tickfont=list(size = 12)),
             yaxis = list(title = "",tickfont=list(size = 8)))

```
